% vim:ft=tex


\documentclass[a4paper,11pt,color,final]{moderncv}

\moderncvtheme[blue]{casual}

\usepackage[utf8]{inputenc}

\usepackage[scale=0.725]{geometry}
\recomputelengths

\firstname{Michael}
\familyname{Richer}
\title{PhD Candidate}
\email{richerm@mcmaster.ca}
\extrainfo{\href{https://www.mricher.net/}{www.mricher.net}}

\begin{document}

\maketitle

\section{Education}

\cventry{2015--present}{PhD chemistry}{McMaster University}{Hamilton, ON}{present candidate}{}

\cventry{2011--2015}{BSc chemistry}{Laurentian University}{Sudbury, ON}{\textit{magna cum laude}}{}

\closesection{}

\section{Employment}

\cventry{2015--present}{Teaching assistant}{McMaster University}{Hamilton, ON}{}{
    TA for introductory chemistry, quantum chemistry, and applied math and software development
    courses. Conduct laboratory demonstrations, supervise students, and teach supplementary
    material.
}

\cventry{2015--present}{Research}{McMaster University}{Hamilton, ON}{}{
    Develop algorithms and software for modeling the quantum electronic structure of molecules,
    with aim to make accurate and robust methods more efficient.
}

\cventry{2014--2015}{Teaching assistant}{Laurentian University}{Sudbury, ON}{}{
    Supervised students and conducted demonstrations for organic chemistry laboratories.
}

\cventry{2014--2015}{Research}{Laurentian University}{Sudbury, ON}{}{
    Wrote software and performed simulations of polymers attached to surfaces in order to predict
    their properties.
}

\section{Skills}

\subsection{Languages}

\cvitem{English}{Fluent; native language}
\cvitem{French}{Fluent; excellent reading/writing, good speaking/listening}

\subsection{Computers}

\cvitem{Management}{Manage small software projects with a team of developers}
\cvitem{Programming}{Numerical computing in C++, Fortran, Python, Julia}
\cvitem{Typesetting}{Latex and troff/groff typesetting systems}
\cvitem{SysAdmin}{System administration on Unix-like operating systems}

\subsection{Laboratory}

\cvitem{Techniques}{Analytical chemistry, inorganic synthesis, IR and NMR spectrometry}
\cvitem{Teaching}{Experienced with teaching laboratory skills and safety}

\pagebreak

\section{Publications}

\cvitem{2022}{
Fanwang Meng, Michael Richer, Alireza Tehrani, Jonathan La, Taewon David Kim, Paul W Ayers, and
Farnaz Heidar-Zadeh.
\textbf{Procrustes: a Python library to find transformations that maximize the similarity between
matrices.}
\emph{Computer Physics Communications}, 108334, 2022.
\href{http://doi.org/10.1016/j.cpc.2022.108334}{doi:10.1016/j.cpc.2022.108334}}

\cvitem{2021}{
Taewon David Kim, Michael Richer, Gabriela Sánchez-Díaz, Farnaz Heidar-Zadeh, Toon
Verstraelen, Ramón Alain Miranda-Quintana, and Paul W Ayers.
\textbf{FanPy: a Python library for prototyping multideterminant methods in ab initio quantum
chemistry.}
\emph{arXiv preprint}, 2021.
\href{https://arxiv.org/abs/2102.01224}{arXiv:2102.01224}}

\cvitem{2021}{
Taewon David Kim, Ramón Alain Miranda-Quintana, Michael Richer, and Paul W Ayers.
\textbf{Flexible ansatz for N-body configuration interaction.}
\emph{Computational and Theoretical Chemistry}, 1202:113–187, 2021.
\href{https://doi.org/10.1016/j.comptc.2021.113187}{doi:10.1016/j.comptc.2021.113187}}

\cvitem{2021}{
Toon Verstraelen, William Adams, Leila Pujal, Alireza Tehrani, Braden D Kelly, Luis Macaya, Fanwang
Meng, Michael Richer, Raymundo Hernández-Esparza, Xiaotian Derrick Yang, and others.
\textbf{IOData: a Python library for reading, writing, and converting computational chemistry file
formats and generating input files.}
\emph{Journal of Computational Chemistry}, 42(6):458–464, 2021.
\href{https://doi.org/10.1002/jcc.26468}{doi:10.1002/jcc.26468}}

\cvitem{2017}{
Paul A Johnson, Peter A Limacher, Taewon D Kim, Michael Richer, Ramón Alain Miranda-Quintana, Farnaz
Heidar-Zadeh, Paul W Ayers, Patrick Bultinck, Stijn De Baerdemacker, and Dimitri Van Neck.
\textbf{Strategies for extending geminal-based wavefunctions: open shells and beyond.}
\emph{Computational and Theoretical Chemistry}, 1116:207–219, 2017.
\href{https://doi.org/10.1016/j.comptc.2017.05.010}{doi:10.1016/j.comptc.2017.05.010}}

\cvitem{2016}{
Farnaz Heidar-Zadeh, Michael Richer, Stijn Fias, Ramón Alain Miranda-Quintana, Matthew Chan, Marco
Franco-Pérez, Cristina E González-Espinoza, Taewon David Kim, Caitlin Lanssens, Anand HG Patel, and
others.
\textbf{An explicit approach to conceptual density functional theory descriptors of arbitrary
order.}
\emph{Chemical Physics Letters}, 660:307–312, 2016.
\href{https://doi.org/10.1016/j.cplett.2016.07.039}{doi:10.1016/j.cplett.2016.07.039}}

\closesection{}


\end{document}
